---
title       : Developing Data Products
subtitle    : Course Project
author      : nuneshub
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
ext_widgets : {rCharts: ["libraries/morris"]}
knit        : slidify::knit2slides
---



```{r setup,echo=FALSE}
library(knitr)
options(width = 100)
opts_chunk$set(message=F,error=F,warning=F,comment=NA,
               tidy=F,cache.path='.cache/',fig.path='fig/')

options(xtable.type = 'html')
knit_hooks$set(inline = function(x) {
    if(is.numeric(x)) {
        round(x, getOption('digits'))
    } else {
        paste(as.character(x), collapse = ', ')
    }
})
```


```{r dataProcessing,echo=FALSE,message=FALSE}
# Load file for processing data
source("slidifyHelper.R")
```



## Shiny Application Summary

* Loads financial markets data of equity indices using the R package `quantmod`.
* User visualise data in interactive plot and may switch to data set tabs to inspect data.

### Inputs: Indices & Time range

* Three equity indices: NASDAQ 100 (US), FTSE 100 (UK) and CAC 40 (France).
* Time range starts on 2013-12-31, in order to avoid heaviness dealing with very long series. 

### Outputs: Main plot & Data sets

* Main plot using `rCharts` / plotting package `morris`.
* Data sets from quantmod for the selected indices presented in different tabs using `dTable`.

#### Link to Shiny App: <https://nuneshub.shinyapps.io/project>

--- .class #id 




## Shiny App Layout 65 fig & lectures

<img class=center src=fig/ShinyAppLayout65pc.bmp height=550>

--- .class #id 




## OUTPUT: Main Plot

### Example for indices: NASDAQ 100 (code NDX) and CAC 40 (code FCHI)

```{r, echo=FALSE,results='asis'}
p <- mPlot(x="date",y=c(colnames(dat)[5],colnames(dat)[11]),
           data=dat,type="Line")
p$set(pointSize=0,lineWidth=3)
p$set(hideHover="auto")
p$save("fig/mainPlot.html",cdn=TRUE)
cat('<iframe src="fig/mainPlot.html" width=100%, height=600></iframe>')
```

--- .class #id 




## OUTPUT: Data Sets

### Example for the NASDAQ data (code NDX)

```{r, echo=FALSE,results='asis'}
dTable(dat1,sPaginationType="full_numbers")
```

















